---
output: github_document
title: "mars2mull"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## mars2mull

The **mars2mull** package contains example XRPD data required for the Digital soil mineralogy with R course. The data consist of 774 diffractograms from across Scotland, and 31 diffractograms from the NASA's Mars Science Laboratory (MSL) onboard the Curiosity Rover. 

The Mars Science Laboratory data were downloaded from the [Geosciences Data Volume](https://pds-geosciences.wustl.edu/msl/msl-m-chemin-4-rdr-v1/) on 14.07.21.

## Installation

The **mars2mull** package can be installed from GitHub using the **devtools** package:

```{r, eval = FALSE}
#Install devtools if you don't already have it on your machine
install.packages("devtools")

#Use the install_github function to install the package
devtools::install_github('benmbutler/mars2mull')
```

The four datasets included within the package are:

1. `scotland_xrpd`: 774 diffractograms of soils sampled from across Scotland.
2. `scotland_locations`:  The locations of the 774 diffractograms sampled from across Scotland
3. `mars_xrpd`: 31 diffractograms of scooped and drilled samples from the MSL
4. `mars_id`: The names and unique IDs of the MSL data along with the sample type and the sampling day (a Martian sol).

The data can be loaded into R using:

```{r, eval = FALSE}
data("scotland_xrpd")
data("scotland_locations")
data("mars_xrpd")
data("mars_id")
```



